---
title: "Demand Graphs - Dry Dinner Pasta"
author: "Xiliang Lin"
date: "3/3/2017"
output: pdf_document
---

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(dev = 'pdf')
knitr::opts_knit$set(root.dir = '~/PassThrough')
estimate_dir = "Data/Demand-Estimates/LogLog-FE/"
iv_estimate_dir = "Data/Demand-Estimates/LogLog-Hausman/"
fun_dir = "Scripts/bin/"
graph_dir = "Results/Demand-Estimates/Tabfigs"
module = 1340

# Useful Libraries
library(data.table)
setNumericRounding(0)
library(ggplot2)
library(grid)
library(gridExtra)
```

## Demand Specification
In this excercise, I estimate demand based on a panel specification. The demand is estimated at market level with defined as the combination of DMA and Chain. We restrict to market with at least 3 stores in the top 90 percent of stores in terms of sales in the category. For each market and brand $k$, we run the regression
$$ \begin{aligned}
y_{sjt} =& \alpha_s + \beta_1 \ln p_{sjt} + \beta_2 \mathbb{I}_{p_{sjt}\ge p_{sj,t-1}}(\ln p_{sjt} - \ln p_{sj,t-1}) + \beta_3 \mathbb{I}_{p_{sjt} < p_{sj,t-1}} (\ln p_{sjt} - \ln p_{sj,t-1}) \\ 
& + \beta_4 \ln (\text{other price}) + \beta_5 \text{promotion} + \beta_6 \text{Seasonality} + \beta_7 \text{Time Trend, 7 degree polyomial}
\end{aligned} $$

```{r}
cvars = c("lprice", "labove_ref", "lbelow_ref", "lother_price", "promotion", "Christmas", "Thanksgiving", "Easter")
clabel = c("Price", "Above Reference Price", "Below Reference Price", "Competitor Price", 
           "Promotion", "Christmas", "Thanksgiving", "Easter")
```

## Demand Estimates Using Prices - No Instrumental Variables
```{r, include=FALSE}
# Load Data
load(paste0(estimate_dir, module, ".RData"))
setkey(estimates, brand_descr_corrected, var_name, grp_id)
# Throw away 1% data for ploting purpose
estimates[, `:=`(bhat_min = quantile(bhat, 0.005),
                 bhat_max = quantile(bhat, 0.995)), 
          by = c("brand_descr_corrected", "var_name")]
estimates = estimates[bhat_min<=bhat & bhat<=bhat_max, ]
```

Plot the estimates regardless of statistical significance. Results are shown below:

```{r, fig.width = 7, fig.height = 9, echo=FALSE, comment=NA, message=FALSE}
bnames = setdiff(unique(estimates$brand_descr_corrected), "OTHER")
gph = as.list(NULL)
nr = ceiling(length(cvars)/2)
nc = ceiling(length(cvars)/nr)
for (b in bnames){
  k = 0
  for (vn in cvars){
    k = k+1
    mdx = round(estimates[.(b, vn), median(bhat)], 3)
    gph[[k]] = ggplot(estimates[.(b, vn), ], aes(x=bhat))+geom_histogram(fill="skyblue", bins=30)+ theme_bw() + 
      theme(axis.title=element_text(size=8))+xlab(clabel[k]) + geom_vline(xintercept = mdx, color="red")
  }
  multplot = marrangeGrob(gph, ncol=nc, nrow=nr, top=b)
  ggsave(paste(graph_dir, "/figs/Demand-NoIV-", b, ".pdf", sep=""), multplot, width=6, height=12)
  invisible(cat('\n'))
  print(multplot)
  invisible(cat("\n"))
  invisible(cat("-------"))
  gph = as.list(NULL)
}
```

## Demand Estimates Using Prices - Hausman Instruments
```{r, include=FALSE}
# Load Data
load(paste0(iv_estimate_dir, module, ".RData"))
setkey(estimates, brand_descr_corrected, var_name, grp_id)
# Throw away 1% data for ploting purpose
estimates[, `:=`(bhat_min = quantile(bhat, 0.005),
                 bhat_max = quantile(bhat, 0.995)), 
          by = c("brand_descr_corrected", "var_name")]
estimates = estimates[bhat_min<=bhat & bhat<=bhat_max, ]
```

```{r, fig.width = 7, fig.height = 9, echo=FALSE, comment=NA, message=FALSE}
bnames = setdiff(unique(estimates$brand_descr_corrected), "OTHER")
gph = as.list(NULL)
nr = ceiling(length(cvars)/2)
nc = ceiling(length(cvars)/nr)
for (b in bnames){
  k = 0
  for (vn in cvars){
    k = k+1
    mdx = round(estimates[.(b, vn), median(bhat)], 3)
    gph[[k]] = ggplot(estimates[.(b, vn), ], aes(x=bhat))+geom_histogram(fill="skyblue", bins=30)+ theme_bw() + 
      theme(axis.title=element_text(size=8))+xlab(clabel[k]) + geom_vline(xintercept = mdx, color="red")
  }
  multplot = marrangeGrob(gph, ncol=nc, nrow=nr, top=b)
  ggsave(paste(graph_dir, "/figs/Demand-HausmanIV-", b, ".pdf", sep=""), multplot, width=6, height=12)
  invisible(cat('\n'))
  print(multplot)
  invisible(cat("\n"))
  invisible(cat("-------"))
  gph = as.list(NULL)
}
```
